Palmer amaranth (\emph{Amaranthus palmeri}) adaptation to US Midwest agroecosystems

### 2022-02-28 Manuscript/Manuscript.tex
as

A Palmer amaranth accession (Kei3) from Perkins County, Nebraska with no
glyphosate resistance was selected for this study (Oliveira et al.,
2021). Three weeks prior to the establishment of each cohort, seeds were
planted in plastic trays containing potting-mix. Emerged seedlings (1
cm) were transplanted into 200 cm\textsuperscript{-3} plastic pots (a
plant pot\textsuperscript{-1}). Palmer amaranth seedlings were supplied
with adequate water and kept under greenhouse conditions at the
University of Wisconsin-Madison, University of Nebraska-Lincoln, and
Western Illinois University; and kept outdoors at the Perkins extension
office in Grant, NE until the 2-3 leaf stage (5 to 8 cm height) when
they were transported to the field.

@@

The initiation and duration of Palmer amaranth flowering was strongly
influenced by cohort and surrounding vegetation (Figure 4A, 4B). In the
first cohort, floral initiation (10\% flowering) occurred near the end
of June for all three treatments, at doy 180, 180.9, and 181.7 for
soybean, bareground, and corn, respectively. In the second cohort,
floral initiation occurred earlier on plants growing in the bareground
than plants growing in soybean or corn (doy 203.8 versus doy 210.9 or
216.8, respectively). Palmer amaranth growing in the bareground had the
shortest duration of floral initiation (measured as the difference
between 10\% and 90\% cumulative flowering) in both the first (34 days)
and second (28 days) cohorts. Palmer amaranth growing in soybean had a
shorter duration of flowering than corn in the first cohort (40 days vs
71 days), but a longer duration in the second cohort (50 vs 44 days).

Palmer amaranth cumulative flowering in the second cohort ranged from
mid July to mid September (Figure 4B). Palmer amaranth growing in the
bareground resulted in earlier flowering time compared to soybean and
corn. Palmer amaranth growing in bareground reached 10\%, 50\%, and 90\%
flowering time at day 203.8, 214.4, and 232.2, respectively. Palmer
amaranth growing in soybean reached 10\% flowering at doy 210.9, which
was 6 days prior to corn (\emph{P}-value = 0.00). Similar trend was
observed at 50\% flowering, whereas Palmer amaranth reached 50\%
flowering in corn (doy 233.0) 4 days after soybeans (doy 228.9; \emph{P}
= 0.00). The 90\% Palmer amaranth cumulative flowering occurred at same
day in corn (260.9) and soybean (260.5; \emph{P} = 0.66).

@@

The model goodness of fit was 0.23, 0.32, 0.40 using pseudo R-squared
test from McFadden, Cox and Snell, and Cragg and Uhler, respectively.
The likelihood ratio test showed a p-value of \textless{} 0.00. The
average marginal effects showed that Palmer amaranth growing in corn
resulted in 14.8\% fewer females plants (Table 2). Moreover, increasing
a cumulative flowering unit doy increases the probability of having a
female plant by 0.4\% (Table 2 and Figure5A). A similar trend was
observed for weight (Figure 5B) and height (Figure 5C), where the
probability of being female increased 0.1\% and 0.2\% for each unit
increase of weight (g) and height (cm), respectively (Table 2).

@@

Our study confirmed that Palmer amaranth is well adapted to growing
throughout the Midwestern United States, and is simply limited in its
range by seed dispersal (Davis et al.~2015). We also confirmed Palmer
amaranth's extraordinary plasticity to adapt to different
agroecosystems. For example, Palmer amaranth mimicked crop architecture
in competing for light (Figure 6), where plants growing in corn
allocated resources to height, while plants growing in bareground
allocated resources to numerous branches. Plants growing in the absence
of a crop produced the greatest biomass, responding to a greater
abundance of light, nutrient and water resources (Figure 3A, 3B). These
results support the argument that Palmer amaranth can quickly evolve
life-history traits to adapt to different cultural practices, similar to
observations in a Palmer amaranth response to nitrogen study (Bravo et
al., 2018). Our results highlight Palmer amaranth as a threat to field
crops as breeding more competitive crop varieties is likely to select
more competitive weed biotypes (Bravo et al., 2017).

Palmer amaranth growth and development in second cohort was limited due
to the crop competitive ability at advanced development stages. Plants
were transplanted at greater crop height and width, which reduced Palmer
amaranth competitiveness. As a result, Palmer amaranth height and
biomass was lower compared to its first cohort. Moreover, Palmer
amaranth growing without crop competition produced the highest amounts
of biomass. The Palmer amaranth strategy in bareground was to invest
biomass in growing plant width and height. Nonetheless, Palmer amaranth
produced 17\% less biomass in second cohort compared to first cohort
timing. In a bareground study, early emerged Palmer amaranth without
competition was 50\% taller than late emerged plants (Webster and Grey,
2015). These results suggest that crop competition is not the only
factor limiting late Palmer amaranth establishment. The limited growth
of Palmer amaranth at second cohort is likely a reduced plant response
to day length, light availability and thermal units (e.g, growing degree
days). The \emph{Amaranthus} species are sensitive to photoperiod (Wu
and Owen, 2014). It is hypothesize that reduced day length or
red/far-red effect contributed to smaller plants at second cohort
regardless the crop. A study in North Carolina and Illinois predicted
that less than 10\% Palmer amaranth seedlings emergence occurred after
June (Piskackova et al., 2021). In addition, Palmer amaranth negative
impact on soybean (Korres et al., 2020) and cotton (Webster and Grey,
2015) yields was higher when plants were established near to crop
planting. Therefore, early management is a key strategy to minimize the
damaging impact of Palmer amaranth to US Midwest cropping systems.

Seed production was not evaluated due to plant harvest at initiation of
flowering. Nonetheless, it is well documented a strong positive
correlation between Palmer amaranth biomass and seed production
(Schwartz et al., 2016; Spaunhorst et al., 2018). In our study, plants
growing from the first cohort accumulated 42\% more biomass when
compared to the second cohort. Therefore, Palmer amaranth plants growing
in the second cohort is likely to produce less seeds regardless the
crop. Our observation is consistent with the findings that the first
Palmer amaranth cohort produced 50\% more seeds per plant than Palmer
amaranth plants established six weeks later in bareground (Webster and
Grey, 2015). Still, seed production at the second cohort will replenish
the soil seedbank. Seed production and deposition in the seedbank is
also a key factor for species perpetuation (Menges, 1987). Palmer
amaranth can produce a hundred thousands seeds per plant (Schwartz et
al., 2016; Keeley et al., 1987), which can stay viable in the soil
seedbank for at least 36 months (Sosnoskie et al., 2013). Therefore,
preventing Palmer amaranth seed production or/and seed migration to
non-native habitats is an essential strategy to minimize the species
impact in agroecosystems (Davis et al., 2015).

Floral initiation depends on the complex interaction between a plant's
genetic makeup and environmental conditions (Lang, 1965). We observed a
significant disruption in flowering caused by surrounding vegetation and
cohort timing. Although all three treatments began flowering at the same
time in the first cohort (about doy 180), it took much less time for the
bareground treatment to reach 90\% flowering (34 days versus 40 for
soybean and 71 for corn). The lack of competition (and stress) in the
bareground resulted in plants that flowered earlier, and were they not
harvested, would have had longer reproductive periods, thereby producing
more seed. Similarly, in the second cohort, the window for all plants to
initiate flowering was much shorter for the bareground (28 days)
compared to Palmer amaranth in soybean (50 days) or corn (44 days).
Significantly, plants in the bareground treatment flowered one week
earlier than soybean, and almost two weeks earlier than corn, again
allowing for greater seed production per plant had they not been
harvested at initial flowering. In some cases, early flowering may
confer an evolutionary advantage, provided the plant has an
indeterminate habit and flowering does not restrict plant growth. In an
Iowa study, Palmer amaranth initiated flowering two weeks prior to
waterhemp (Baker, 2021), and this characteristic may partially explain
why Palmer amaranth can displace waterhemp where both occur in the same
agronomic field. In other cases, however, early flower initiation may be
a response to stressful conditions as a plant attempts to reproduce
before running out of resources. In a dioecious species like Palmer
amaranth, exerting stress on plants to manipulate flowering may be
beneficial in limiting seed production (McFarlane et al., 2018;
Schliekelman et al., 2005). For example, when growing under water
stress, there was a seven days flowering mismatch between male and
female plants (Mesgaran et al., 2021), which can minimize plant
outcrossing, reduce seed production and the exchange of resistant
alleles (Jhala et al., 2021). In our study we observed

An ecological approach to reduce Palmer amaranth seed production is
understanding plant biology, including flowering pattern. Our study
suggests that Palmer amaranth flowering was slightly influenced by crops
and cohort timings. Palmer amaranth growing in bareground and corn
resulted in the overall shortest and longest flowering window,
respectively. The shortest flowering window of second cohorts of Palmer
amaranth growing in bareground highlighted the impact of photoperiod on
flowering. When growing in soybean, Palmer amaranth flowering window was
similar to bareground for the first cohort but similar to corn at second
cohort timing. Plant flowering initiation is complex and depends on the
complex interaction between genetic makeup and the environmental
conditions (Lang, 1965). We hypothesize that when growing in high
competition (e.g., second cohort), Palmer amaranth plants tend to
initiate flowering early, as well as having an extended flowering
window. A study has shown that Palmer amaranth initiated flowering two
weeks prior to the native waterhemp in Iowa (Baker, 2021). Early flower
initiation could also be a plant strategy when growing in stressful
conditions. For example, when growing under water stress, early
flowering in Palmer amaranth resulted in a mismatch between female and
male plants by seven days (Mesgaran et al., 2021). A mismatch in Palmer
amaranth male and female flowering period can minimize plant
outcrossing, reducing plant seed production and/or exchange of resistant
alleles (Jhala et al., 2021). Sex dimorphism manipulation is considered
a potential ecological pest control strategy (McFarlane et al., 2018;
Schliekelman et al., 2005).

The mechanisms of gender-determination in plant species is intriguing
and has arouse the curiosity of many scientists, including Charles
Darwin (Darwin, 1888). In our study, the gender model performance was
decent (AUC 0.64) considering the biology of plant flowering. A 1:1 male
and female sex ratio is a general an evolutionarily stable strategy for
plant species perpetuation (Fisher, 1930). However, a slight deviation
from 1:1 sex ratio occurs in some dioecious species. For example, the
dioecious \emph{Halophila stipulacea} is a female-biased plant in its
native habitat, but the naturalized \emph{H. stipulacea} has a 1:1 ratio
(Nguyen et al., 2018). Naturalization of \emph{H. stipulacea} reduced
female-male ratio to expand into its non-native habitat (Nguyen et al.,
2018). Also, biotic and/or abiotic stress can influence plant gender
determination. Palmer amaranth male-to-female ratio was greater under
high plant densities (Korres and Norsworthy, 2017) and after herbicide
application (Rumpa et al., 2019). We observed sexual dimorphism in
Palmer amaranth in response to surrounding vegetation and plant
morphological attributes. Our model estimated that late flowering,
heavier and taller Palmer amaranth plants slightly deviated from 1:1
ratio in favor of female plants. It was reported that female Palmer
amaranth plants invested more in height, stem and biomass while male
plants invested more in leaf area and leaf dry weight under nutrient
deficiency (Korres et al., 2017). We observed more female plants in
soybean and bareground compared to corn. Palmer amaranth plants in the
corn were more stressed by interspecific competition as evidenced by
less biomass and a lower weight:height ratio. Sexual dimorphism is
documented in other dioecious species (Barrett and Hough, 2013). For
example, stronger female plant competition and greater male tolerance to
herbivory was reported in \emph{Spinacia oleracea} (Pérez-Llorca and
Sánchez Vilas, 2019). Research on candidate genes for sex determination
in \emph{Amaranthus} species are currently underway but is far from
complete (Montgomery et al., 2021, 2019). Further studies are also
needed to understand the ecological basis of Palmer amaranth flowering,
including plant behavior under climate change.

@@

\caption{Mean average temperature (C) and total montly precipitation (mm) at Arlington, WI, Clay Center, NE, Grant, NE, Lincoln, NE and Macomb, IL}\label{fig:Figure-1}
\end{figure}

@@

\caption{Palmer amaranth adaptation study layout of a plant cohort timing in bareground, corn, and soybean. Twenty-four Palmer amaranth plants were place 76.2 cm apart in each field experimental unit}\label{fig:Figure-2}
\end{figure}

@@

\caption{Palmer amaranth biomass (A) and height (B) growing in corn, bareground, and soybean nested across Arlington, WI, Clay Center, NE, Grant, NE, Lincoln, NE and Macomb, IL}\label{fig:Figure-3}
\end{figure}

@@

\caption{Cumulative flowering of Palmer amaranth at first and second transplant timing (A) and day of year of 10, 50, and 90 cumulative flowering at first and second cohort transplanting time (B) nested across Arlington, WI, Clay Center, NE, Grant, NE, Lincoln, NE and Macomb, IL}\label{fig:Figure-4}
\end{figure}

@@

\caption{The probability (P) of being female Palmer amaranth by day of year (A), weight (B), and height (C). Black line represents the model estimation and shaded green the confidence intervals}\label{fig:Figure-5}
\end{figure}

@@

\caption{MCO (180 cm) holds harvested Palmer amaranth plants at 40 days after first cohort transplanting (A) and 33 days after second cohort transplanting (B) time. From left to right in each image, Palmer amaranth growing in bareground, soybean and corn in Arlington, Wisconsin}\label{fig:Figure-6}
\end{figure}

>>>>

A Palmer amaranth accession (Kei3) from Perkins County, Nebraska
susceptible to glyphosate was selected for this study (Oliveira et al.,
2021). Three weeks prior to the establishment of each cohort, seeds were
planted in plastic trays containing potting-mix. Emerged seedlings (1
cm) were transplanted into 200 cm\textsuperscript{-3} plastic pots (one
plant pot\textsuperscript{-1}). Palmer amaranth seedlings were supplied
with adequate water and kept under greenhouse conditions at the
University of Wisconsin-Madison, University of Nebraska-Lincoln, and
Western Illinois University; and kept outdoors at the Perkins Extension
office in Grant, NE until the 2-3 leaf stage (5 to 8 cm height) when
they were transported to the field.

@@

The initiation and duration of Palmer amaranth flowering were strongly
influenced by cohort and surrounding vegetation (Figure 4A, 4B). In the
first cohort, floral initiation (10\% flowering) occurred near the end
of June for all three treatments, at doy 180, 180.9, and 181.7 for
soybean, bareground, and corn, respectively. In the second cohort,
floral initiation occurred earlier on plants growing in the bareground
than plants growing in soybean or corn (doy 203.8 versus doy 210.9 or
216.8, respectively). Palmer amaranth growing in the bareground had the
shortest flowering initiation (measured as the difference between 10\%
and 90\% cumulative flowering) in both the first (34 days) and second
(28 days) cohorts. Palmer amaranth growing in soybean had a shorter
duration of flowering than corn in the first cohort (40 days vs 71
days), but a longer duration in the second cohort (50 vs 44 days).

Palmer amaranth cumulative flowering in the second cohort occurred from
mid July to mid September (Figure 4B). Palmer amaranth growing in the
bareground resulted in earlier flowering time compared to soybean and
corn. Palmer amaranth growing in bareground reached 10\%, 50\%, and 90\%
flowering time at day 203.8, 214.4, and 232.2, respectively. Palmer
amaranth growing in soybean reached 10\% flowering at doy 210.9, which
was 6 days prior to corn (\emph{P}-value = 0.00). Similar trend was
observed at 50\% flowering, whereas Palmer amaranth reached 50\%
flowering in corn (doy 233.0) 4 days after soybeans (doy 228.9; \emph{P}
= 0.00). The 90\% Palmer amaranth cumulative flowering occurred at same
day in corn (260.9) and soybean (260.5; \emph{P} = 0.66).

@@

The model goodness of fit was 0.23, 0.32, 0.40 using pseudo R-squared
test from McFadden, Cox and Snell, and Cragg and Uhler, respectively.
The likelihood ratio test showed a p-value of \textless{} 0.00. The
average marginal effects showed that Palmer amaranth growing in corn
resulted in 14.8\% fewer females plants (Table 2). Moreover, increasing
a cumulative flowering unit doy increases the probability of having a
female plant by 0.4\% (Table 2 and Figure5A). A similar trend was
observed for weight (Figure 5B) and height (Figure 5C), where the
probability of being female increased 0.1\% and 0.2\% for each unit
increase of weight and height, respectively (Table 2).

@@

Our study demonstrate that Palmer amaranth is well adapted to growing
conditions throughout the Midwestern United States, and is simply
limited in its range by seed dispersal (Davis et al.~2015). We also
confirmed Palmer amaranth's extraordinary plasticity to adapt to
different agroecosystems. For example, Palmer amaranth mimicked crop
architecture in competing for light (Figure 6), where plants growing in
corn allocated resources to height, while plants growing in bareground
allocated resources to numerous branches. Plants growing in the absence
of a crop produced the greatest biomass, responding to a greater
abundance of light, nutrient and water resources (Figure 3A, 3B). These
results support the argument that Palmer amaranth can quickly evolve
life-history traits to adapt to different cultural practices, similar to
observations in a Palmer amaranth response to nitrogen study (Bravo et
al., 2018). Our results highlight Palmer amaranth as a threat to field
crops and breeding more competitive crop varieties is likely to select
more competitive weed biotypes (Bravo et al., 2017).

Palmer amaranth growth and development in the second cohort was limited
due to the crop competitive ability at advanced developmental stages.
Palmer amaranth seedling were transplanted at greater crop height and
width, which reduced Palmer amaranth competitiveness. As a result,
Palmer amaranth height and biomass were lower compared to its first
cohort. Moreover, Palmer amaranth growing without crop competition
produced the highest amounts of biomass. The Palmer amaranth strategy in
bareground was to invest biomass in growing plant width and height.
Nonetheless, Palmer amaranth produced 17\% less biomass in second cohort
compared to first cohort timing. In a bareground study, early emerged
Palmer amaranth without competition was 50\% taller than late emerged
plants (Webster and Grey, 2015). These results suggest that crop
competition is not the only factor limiting late Palmer amaranth
establishment. The limited growth of Palmer amaranth at second cohort is
likely a reduced plant response to day length, light availability and
thermal units (e.g, growing degree days). The \emph{Amaranthus} species
are sensitive to photoperiod (Wu and Owen, 2014). We hypothesize that
reduced day length or red/far-red effect contributed to smaller plants
at second cohort regardless the crop. A study in North Carolina and
Illinois predicted that less than 10\% Palmer amaranth seedlings
emergence occurred after June (Piskackova et al., 2021). In addition,
Palmer amaranth negative impact on soybean (Korres et al., 2020) and
cotton (Webster and Grey, 2015) yields was higher when plants were
established close to crop planting. Therefore, early season management
is a key strategy to minimize the damaging impact of Palmer amaranth to
US Midwest cropping systems.

Seed production was not evaluated due to plant harvest at initiation of
flowering. Nonetheless, a strong positive correlation between Palmer
amaranth biomass and seed production has been documented (Schwartz et
al., 2016; Spaunhorst et al., 2018). In our study, plants growing from
the first cohort accumulated 42\% more biomass when compared to the
second cohort. Therefore, Palmer amaranth plants growing in the second
cohort are likely to produce fewer seeds regardless of crop. Our
observation is consistent with the findings that the first Palmer
amaranth cohort produced 50\% more seeds per plant than Palmer amaranth
plants established six weeks later in bareground (Webster and Grey,
2015). Still, seed production at the second cohort will replenish the
soil seedbank. Seed production and deposition in the seedbank is also a
key factor for species perpetuation (Menges, 1987). Palmer amaranth can
produce more than hundred thousands seeds per plant (Schwartz et al.,
2016; Keeley et al., 1987), which can stay viable in the soil seedbank
for at least 36 months (Sosnoskie et al., 2013). Therefore, preventing
Palmer amaranth seed production or/and seed migration to non-native
habitats is an essential strategy to minimize the species impact in
agroecosystems.

An ecological approach to reduce Palmer amaranth seed production
encompasses understanding plant biology, including flowering pattern.
Floral initiation depends on the complex interaction between a plant's
genetic makeup and environmental conditions (Lang, 1965). We observed a
significant disruption in flowering caused by surrounding vegetation and
cohort timing. Although all three treatments began flowering at the same
time in the first cohort (about doy 180), it took much less time for the
bareground treatment to reach 90\% flowering (34 days versus 40 for
soybean and 71 for corn). The lack of competition (and stress) in the
bareground resulted in plants that flowered earlier, and were they not
harvested, would have had longer reproductive periods, thereby producing
more seed. Similarly, in the second cohort, the window for all plants to
initiate flowering was much shorter for the bareground (28 days)
compared to Palmer amaranth in soybean (50 days) or corn (44 days).
Significantly, plants in the bareground treatment flowered one week
earlier than soybean, and almost two weeks earlier than corn, again
allowing for greater seed production per plant had they not been
harvested at initial flowering. In some cases, early flowering may
confer an evolutionary advantage, provided the plant has an
indeterminate habit and flowering does not restrict plant growth. In
other cases, however, early flower initiation may be a response to
stressful conditions as a plant attempts to reproduce before running out
of resources. In an Iowa study, Palmer amaranth initiated flowering two
weeks prior to waterhemp (Baker, 2021), and this characteristic may
partially explain why waterhemp can displace Palmer amaranth in Iowa,
where Palmer amaranth is not well adapted. In a dioecious species like
Palmer amaranth, exerting stress on plants to manipulate flowering may
be beneficial in limiting seed production (McFarlane et al., 2018;
Schliekelman et al., 2005). For example, when growing under water
stress, there was a seven days flowering mismatch between male and
female plants (Mesgaran et al., 2021), which can minimize plant
outcrossing, reduce seed production and the exchange of resistant
alleles (Jhala et al., 2021).

The mechanisms of gender-determination in plant species is intriguing
and has arouse the curiosity of many scientists, including Charles
Darwin (Darwin, 1888). In our study, the gender model performance was
decent (AUC 0.64) considering the biology of plant flowering. A 1:1 male
and female sex ratio is a general and evolutionarily stable strategy for
plant species perpetuation (Fisher, 1930). However, a slight deviation
from 1:1 sex ratio occurs in some dioecious species. For example, the
dioecious \emph{Halophila stipulacea} is a female-biased plant in its
native habitat, but the naturalized \emph{H. stipulacea} has a 1:1 ratio
(Nguyen et al., 2018). Naturalization of \emph{H. stipulacea} reduced
female-male ratio to expand into its non-native habitat (Nguyen et al.,
2018). Also, biotic and/or abiotic stress can influence plant gender
determination. Palmer amaranth male-to-female ratio was greater under
high plant densities (Korres and Norsworthy, 2017) and after herbicide
application (Rumpa et al., 2019). We observed sexual dimorphism in
Palmer amaranth in response to surrounding vegetation and plant
morphological attributes. Our model estimated that late flowering,
heavier and taller Palmer amaranth plants slightly deviated from 1:1
ratio in favor of female plants. It was reported that female Palmer
amaranth plants invested more in height, stem and biomass while male
plants invested more in leaf area and leaf dry weight under nutrient
deficiency (Korres et al., 2017). We observed more female plants in
soybean and bareground compared to corn. Palmer amaranth plants in the
corn were more stressed by interspecific competition as evidenced by
less biomass and a lower weight:height ratio. Sexual dimorphism is
documented in other dioecious species (Barrett and Hough, 2013). For
example, stronger female plant competition and greater male tolerance to
herbivory was reported in \emph{Spinacia oleracea} (Pérez-Llorca and
Sánchez Vilas, 2019). Research on candidate genes for sex determination
in \emph{Amaranthus} species are currently underway but is far from
complete (Montgomery et al., 2021, 2019). Further studies are also
needed to understand the ecological basis of Palmer amaranth flowering,
including plant behavior under climate change.

@@

\caption{Mean average temperature (C) and total montly precipitation (mm) at Arlington, WI, Clay Center, NE, Grant, NE, Lincoln, NE and Macomb, IL.}\label{fig:Figure-1}
\end{figure}

@@

\caption{Palmer amaranth adaptation study layout of a plant cohort timing in bareground, corn, and soybean. Twenty-four Palmer amaranth plants were place 76.2 cm apart in each field experimental unit.}\label{fig:Figure-2}
\end{figure}

@@

\caption{Palmer amaranth biomass (A) and height (B) growing in corn, bareground, and soybean nested across Arlington, WI, Clay Center, NE, Grant, NE, Lincoln, NE and Macomb, IL.}\label{fig:Figure-3}
\end{figure}

@@

\caption{Cumulative flowering of Palmer amaranth at first and second transplant timing (A) and day of year of 10, 50, and 90 cumulative flowering at first and second cohort transplanting time (B) nested across Arlington, WI, Clay Center, NE, Grant, NE, Lincoln, NE and Macomb, IL.}\label{fig:Figure-4}
\end{figure}

@@

\caption{The probability (P) of being female Palmer amaranth by day of year (A), weight (B), and height (C). Black line represents the model estimation and shaded green the confidence intervals.}\label{fig:Figure-5}
\end{figure}

@@

\caption{MCO (180 cm) holds harvested Palmer amaranth plants at 40 days after first cohort transplanting (A) and 33 days after second cohort transplanting (B) time. From left to right in each image, Palmer amaranth growing in bareground, soybean and corn in Arlington, Wisconsin.}\label{fig:Figure-6}
\end{figure}
